### 2021-05-11 README.Rmd
Some modifications preparing for further generalizations.

@@

# TasmanianHS.R should be in rundir, but during development is in data-raw
source(paste0(rundir,"/TasmanianHS.R"))
# generate equilibrium zone ----------------------------------------------------
starttime2 <- (Sys.time())
zone <- makeequilzone(rundir,"controlsau.csv",datadir=datadir,cleanslate = TRUE)
equiltime <- (Sys.time()); print(equiltime - starttime2)
# declare main objects ---------------------------------------------------------
glb <- zone$glb
ctrl <- zone$ctrl
zone1 <- zone$zone1
projC <- zone1$projC
condC <- zone1$condC
zoneC <- zone$zoneC
zoneD <- zone$zoneD
product <- zone$product
# add some tables and plots into rundir
biology_plots(rundir, glb, zoneC)
plotproductivity(rundir,product,glb)
numbersatsize(rundir, glb, zoneD)
# Condition on Fishery ---------------------------------------------------------
zoneDD <- dohistoricC(zoneD,zoneC,glob=glb,condC,sigR=1e-08,sigB=1e-08)

propD <- t(getzoneprops(zoneC,zoneDD,glb,year=47))
addtable(round(propD,4),"propertyDD.csv",rundir,category="zoneDD",caption=
           "Properties of zoneD after conditioning on historical catches.")
addtable(round(t(zoneDD$harvestR[40:47,]),4),"final_harvestR.csv",rundir,
         category="zoneDD",caption="Last eight years of harvest rate.")
popdefs <- getlistvar(zone$zoneC,"popdef")
addtable(round(t(popdefs),3),"popdefs.csv",rundir,category="zoneDD",caption=
           "Population specific definitions")
# Prepare projections ----------------------------------------------------------
plotconditioning(zoneDD,glb,zoneC,condC$histCE,1973:2019,rundir)

#explicit definition of indata rather than using the tasdata function
indata <- list(arrce=condC$histCE,yearnames=rownames(condC$histCE),
               acatches=tail(condC$histCatch,1),fis=NULL,nas=NULL)
cmcda <- mcdahcr(indata,hsargs=hsargs,saunames=glb$saunames)
pms <- cmcda$pms
multTAC <- cmcda$multTAC
out <- prepareprojection(projC=projC,condC=condC,zoneC=zoneC,glb=glb,
                            multTAC=multTAC,zoneDD=zoneDD,ctrl=ctrl,varyrs=7,
                            lastsigR = ctrl$withsigR)
# prepareprojection needs to be modified so that is uses expected catches rather
# than calculating them internally (which will differ by jurisdiction)
zoneDP <- out$zoneDP
projC <- out$projC
zoneCP <- out$zoneCP
zoneDDR <- out$zoneDDR

zoneDP <- doprojections(ctrl,zoneDP,zoneCP,condC$histCE,glb,mcdahcr,hsargs,
                        tasCPUE,tasFIS,tasNaS)
# save more plots to rundir ----------------------------------------------------
histCE <- condC$histCE
B0 <- getvar(zoneC,"B0")
ExB0 <- getvar(zoneC,"ExB0")
sauout <- sauplots(zoneDP,zoneDDR,glb,rundir,B0,ExB0,startyr=25,addCI=TRUE,
                  histCE=histCE)
diagnosticsproj(sauout$zonePsau,glb,rundir,nrep=3)
outzone <- poptozone(zoneDP,glb,
                     B0=sum(getvar(zoneC,"B0")),
                     ExB0=sum(getvar(zoneC,"ExB0")))
plotZone(outzone,rundir,CIprobs=c(0.05,0.5,0.95),addfile=TRUE)
projtime <- Sys.time()
print(projtime - starttime)
# make results webpage ---------------------------------------------------------
replist <- list(starttime=as.character(starttime),endtime=as.character(projtime))

>>>>

* 2021-05-07 0.0.0.2800

@@

# TasmanianHS.R should be in rundir, but during development is in data-raw
source(paste0(rundir,"/TasmanianHS.R"))
# generate equilibrium zone ----------------------------------------------------
starttime2 <- (Sys.time())
zone <- makeequilzone(rundir,"controlsau.csv",datadir=datadir,cleanslate = TRUE)
equiltime <- (Sys.time()); print(equiltime - starttime2)
# declare main objects ---------------------------------------------------------
glb <- zone$glb
ctrl <- zone$ctrl
zone1 <- zone$zone1
projC <- zone1$projC
condC <- zone1$condC
zoneC <- zone$zoneC
zoneD <- zone$zoneD
product <- zone$product
# add some tables and plots into rundir
biology_plots(rundir, glb, zoneC)
plotproductivity(rundir,product,glb)
numbersatsize(rundir, glb, zoneD)
# Condition on Fishery ---------------------------------------------------------
zoneDD <- dohistoricC(zoneD,zoneC,glob=glb,condC,calcexpectpopC,sigR=1e-08,sigB=1e-08)

propD <- t(getzoneprops(zoneC,zoneDD,glb,year=47))
addtable(round(propD,4),"propertyDD.csv",rundir,category="zoneDD",caption=
           "Properties of zoneD after conditioning on historical catches.")
addtable(round(t(zoneDD$harvestR[40:47,]),4),"final_harvestR.csv",rundir,
         category="zoneDD",caption="Last eight years of harvest rate.")
popdefs <- getlistvar(zone$zoneC,"popdef")
addtable(round(t(popdefs),3),"popdefs.csv",rundir,category="zoneDD",caption=
           "Population specific definitions")
# Prepare projections ----------------------------------------------------------
plotconditioning(zoneDD,glb,zoneC,condC$histCE,rundir)

#explicit definition of indata rather than using the tasdata function
indata <- list(arrce=condC$histCE,yearnames=rownames(condC$histCE),
               acatches=tail(condC$histCatch,1),fis=NULL,nas=NULL)
cmcda <- mcdahcr(indata,hsargs=hsargs,saunames=glb$saunames)
pms <- cmcda$pms
multTAC <- cmcda$multTAC
out <- prepareprojection(projC=projC,condC=condC,zoneC=zoneC,glb=glb,
                         multTAC=multTAC,calcexpectpopC,zoneDD=zoneDD,
                         ctrl=ctrl,varyrs=7,lastsigR = ctrl$withsigR)
# prepareprojection needs to be modified so that is uses expected catches rather
# than calculating them internally (which will differ by jurisdiction)
zoneDP <- out$zoneDP
projC <- out$projC
zoneCP <- out$zoneCP
zoneDDR <- out$zoneDDR

zoneDP <- doprojections(ctrl,zoneDP,zoneCP,condC$histCE,glb,hcrfun=mcdahcr,hsargs,
                        sampleCE=tasCPUE,sampleFIS=tasFIS,sampleNaS=tasNaS,
                        getdata=tasdata,calcpopC=calcexpectpopC)
# save more plots to rundir ----------------------------------------------------
histCE <- condC$histCE
B0 <- getvar(zoneC,"B0")
ExB0 <- getvar(zoneC,"ExB0")
sauout <- sauplots(zoneDP,zoneDDR,glb,rundir,B0,ExB0,startyr=25,addCI=TRUE,
                  histCE=histCE)
diagnosticsproj(sauout$zonePsau,glb,rundir,nrep=3)
outzone <- poptozone(zoneDP,glb,
                     B0=sum(getvar(zoneC,"B0")),
                     ExB0=sum(getvar(zoneC,"ExB0")))
plotZone(outzone,rundir,glb,CIprobs=c(0.05,0.5,0.95),addfile=TRUE)
projtime <- Sys.time()
print(projtime - starttime)
# make results webpage ---------------------------------------------------------
replist <- list(starttime=as.character(starttime),endtime=as.character(projtime))
